Untitled

### 2020-09-10 Rmd/brms_metric_selfing.Rmd
Running brms selfing models, still haver to run them again

This model contains both quantitative and qualitative data of selfing levels and the fixed effect is grouped in 4 categories of high, medium, low and none levels of selfing. The response variable is the integer of visits.

>>>>

This model contains both quantitative and qualitative data of selfing levels and the fixed effect is grouped in 4 categories: "high", "medium", "low" and none levels of selfing. The response variable is the integer of visits. Note that the quantitative measurement that we use is autonomous fruit production.
